Compositional Certified Resource Bounds\ifshort{\vspace{-1.15cm}}{}

### 2014-11-12 paper/main.tex
some formatting

while (x<n) {
  ${\color{blue}%
  x{<}n; \, |[x, n]| {+} |[z, n]| \vdash }$
  if (z>x)
    ${\color{blue}%
    x{<}n; \, |[x, n]| {+} |[z, n]| \vdash }$
    x=x+1;
    ${\color{blue}%
    \dashv \cdot; \, 1 {+} |[x, n]| {+} |[z, n]| }$
  else
    ${\color{blue}%
    z{\leq}x, x{<}n; \, |[x, n]| {+} |[z, n]| \vdash }$
    z=z+1;
    ${\color{blue}%
    \dashv \cdot; \, 1 {+} |[x, n]| {+} |[z, n]| }$
  ${\color{blue}%
  \dashv \cdot; \, 1 {+} |[x, n]| {+} |[z, n]| \vdash }$
  tick(1);
  ${\color{blue}%
  \dashv \cdot; \, |[x, n]| {+} |[z, n]| }$
  }
   \end{lstlisting}
\vspace{-2.5ex}
$|[x, n]| + |[z, n]|$
\\[.4\baselineskip]
      {\bf speed\_2}
    \end{center}
  \end{minipage}
%
\hfill
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
while (z-y>0) {
  ${\color{blue}%
  y{<}z; \, 3.1|[y,z]| {+} 0.1|[0,y]| \vdash }$
  y=y+1;
  ${\color{blue}%
  \dashv \cdot; \, 3 {+} 3.1|[y,z]| {+} 0.1|[0,y]| \vdash }$
  tick(3);
  ${\color{blue}%
  \dashv \cdot; \, 3.1|[y,z]| {+} 0.1|[0,y]| }$
}
${\color{blue}%
\dashv \cdot; \, 3.1|[y,z]| {+} 0.1|[0,y]| \vdash }$
while (y>9) {
  ${\color{blue}%
  y{>}9; \, 3.1|[y,z]| {+} 0.1|[0,y]| \vdash }$
  y=y-10;
  ${\color{blue}%
  \dashv \cdot; \, 1 {+} 3.1|[y,z]| {+} 0.1|[0,y]| \vdash }$
  tick(1);
  ${\color{blue}%
  \dashv \cdot; \, 3.1|[y,z]| {+} 0.1|[0,y]| }$
}
   \end{lstlisting}
\vspace{-2.5ex}
$3.1|[y,z]| + 0.1|[0,y]|$
\\[.4\baselineskip]
      {\bf t08a}
    \end{center}
  \end{minipage}
%
\hfill
%
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
while (n<0) {
  ${\color{blue}%
  n{<}0; \,  P(n,y) \vdash }$
  n=n+1;
  ${\color{blue}%
  \dashv \cdot; \,  59 {+} P(n,y) \vdash }$
  y=y+1000;
  ${\color{blue}%
  \dashv \cdot; \, 9 {+} P(n,y) \vdash }$
  while (y>=100 && *){
    ${\color{blue}%
    y{>}99; \, 9 {+} P(n,y) \vdash }$
    y=y-100;
    ${\color{blue}%
    \dashv \cdot; \, 14 {+} P(n,y) \vdash }$
    tick(5);
  } ${\color{blue}%
  \dashv \cdot; \, 9 {+} P(n,y) \vdash }$
  tick(9);
  ${\color{blue}%
  \dashv \cdot; \, P(n,y) }$
}
   \end{lstlisting}
\vspace{-2.5ex}
$59|[n,0]| {+} 0.05|[0,y]|$
\\[.4\baselineskip]
      {\bf t27}
    \end{center}
  \end{minipage}
\vspace{1ex}
\caption{Derivations of bounds on the number of ticks for challenging
  examples.  Examples \emph{speed\_1} and \emph{speed\_2}
  (from~\cite{GulwaniMC09}) use \emph{tricky iteration patterns},
  \emph{t08a} contains \emph{sequential loops} so that the iterations
  of the second loop depend on the first, and \emph{t27} contains
  interacting \emph{nested loops}. In the potential functions, we only
  mention the non-zero terms and in the logical context $\Gamma$ we
  only mention assertions that we use. In
  Example \emph{t27}, we use the abbreviation $P(n,y) := 59|[n,0]| {+}
  0.05|[0,y]|$.}
  \label{fig:ex_list}
\end{figure*}

@@

\ifshort{
\begin{figure*}
\small
\vspace{-.3cm}
\begin{mathpar}
\Rule{Q:Update}
{ q'_{xy}, q'_{yx} \in \Qplusz
\\ \forall u. (q_{yu} = q'_{xu} + q'_{yu} \land q_{uy} = q'_{ux} + q'_{uy})
}
{ B; R; (\Gamma[x/y], Q {+} M_u {+} M_e(y)) \vdash x \gets y \dashv (\Gamma, Q') }
%
\and \Rule[leftskip=.1cm,rightskip=.1cm]{Q:Loop}
{ (\Gamma', Q'); R; (\Gamma,Q) \vdash S \dashv (\Gamma,  Q {+} M_l) }
{ B; R; (\Gamma, Q) \vdash \code{loop}~S \dashv (\Gamma', Q') }
%
\\ \Rule[leftskip=1cm,rightskip=.5cm]{Q:IncP}
{ \Gamma \models y \ge 0 \!
\\ \mathcal U = \left\{ u \mid \Gamma \models x + y \in \inter x u \right\} \!
\\\\ \textstyle q'_{0y} = q_{0y}
      + \sum_{u \in \mathcal U} q_{xu}
      - \sum_{v \not\in \mathcal U} q_{vx} \!
}
{ \textstyle
  B; R; (\Gamma[x/x {+} y], Q {+} M_u {+} M_e(x {+} y)) \vdash x \gets x + y \dashv (\Gamma, Q')
}
%
\and \Rule[leftskip=.5cm,rightskip=1cm]{Q:Inc}
{ M = M_u + M_e(x {\pm} y)
\\\\ \textstyle q'_{0y} = q_{0y} - \sum_{v} q_{vx}
\\ \textstyle q'_{y0} = q_{y0} - \sum_{v} q_{xv}
}
{ \textstyle
  B; R; (\Gamma[x/x {\pm} y], Q {+} M) \vdash x \gets x \pm y \dashv (\Gamma, Q')
}
%
\\ \Rule{Q:Seq}
{  B; R; (\Gamma, Q) \vdash S_1 \dashv (\Gamma', Q' {+} M_s)
\\\\ B; R; (\Gamma', Q') \vdash S_2 \dashv (\Gamma'',Q'')
}
{ B; R; (\Gamma, Q) \vdash S_1;S_2 \dashv (\Gamma'',Q'') }
%
\and \Rule{Q:Weak}
{ B; R; (\Gamma_2,Q_2) \vdash S \dashv (\Gamma'_2, Q'_2)
\\ \!\! \Gamma_1 \models \Gamma_2
\\\\ Q_1 \succeq_{\Gamma_1} Q_2
\\ \Gamma'_2 \models \Gamma'_1
\\ Q'_2 \succeq_{\Gamma_2'} Q'_1
}
{ B; R; (\Gamma_1,Q_1) \vdash S \dashv (\Gamma'_1, Q'_1) }
%
\\ \Rule{Relax}
{ \mathcal L = \{ xy \mid \exists l_{xy} {\in} \N \, . \, \Gamma \models l_{xy} \le |\inter x y| \}
\\ \mathcal U = \{ xy \mid \exists u_{xy}{\in} \N \, . \, \Gamma \models |\inter x y| \le u_{xy} \}
\\\\ \forall i \in \mathcal U.\, q'_i \ge q_i - r_i
\\ \forall i \in \mathcal L.\, q'_i \ge q_i + p_i
\\ \forall i \not\in \mathcal U {\cup} \mathcal L {\cup} \{0\} .\, q'_i \ge q_i
\\ q'_0 \geq q_0 {\textstyle + \sum_{i \in \mathcal U} u_i r_i - \sum_{i \in \mathcal L} l_i p_i}
}
{ Q' \succeq_\Gamma Q }

\end{mathpar}
\caption{Selected inference rules of the quantitative analysis.}
\label{fig:auto}
\end{figure*}
}{}

@@

@@

\newcommand{\loopbody}[0]{\ensuremath{\code{if~(x - 10 \geq 0)~\{x=x{-}10; tick(5);\}~else~break;}}}
\begin{figure*}
\vspace{-.3cm}
\centering
\footnotesize
\begin{mathpar}
\inferrule*[right={\scriptsize (Q:Loop)},leftskip=0cm,rightskip=0cm,width=20cm]
{ \inferrule*[right={\scriptsize (Q:If)},leftskip=0cm,rightskip=0cm,width=20cm]
  { \inferrule*[right={\scriptsize (Q:Weak)},leftskip=2cm,rightskip=4cm, vdots=1cm]
    { \inferrule*[right={\scriptsize (Q:Seq)},leftskip=0cm,rightskip=0cm]
      { \inferrule*[right={\scriptsize (Q:Weak)},leftskip=0cm,rightskip=0cm]
        { \inferrule*[right={\scriptsize (Q:DecP)},leftskip=0cm,rightskip=0cm]
          {
          }
          { (x {<} 10, B^\text{de}); ((x {\geq} 10,Q^\text{de})  \vdash \code{x = x - 10}
            \dashv (\cdot, P^\text{de})
          }
        }
        { (x {<} 10, B^\text{we}); ((x {\geq} 10,Q^\text{we})  \vdash \code{x = x - 10}
          \dashv (\cdot, P^\text{we})
        }
        \and
        \inferrule*[right={\scriptsize (Q:Tick)},leftskip=0cm,rightskip=0cm]
        {
        }
        { (x {<} 10, B^\text{ti}); (\cdot,Q^\text{ti})  \vdash \code{tick(5)}
          \dashv (\cdot, P^\text{ti})
        }
      }
      { (x {<} 10, B^\text{sq}); ((x {\geq} 10,Q^\text{sq}) \vdash
        \code{x=x{-}10; tick(5);} \dashv (\cdot,P^\text{sq})
      }
    }
    { (x {<} 10, B^\text{if}); ((x {\geq} 10,Q^\text{if}) \vdash
      \code{x=x{-}10; tick(5);} \dashv (\cdot,P^\text{if})
    }
    \and
    \inferrule*[right={\scriptsize (Q:Weak)},leftskip=4.5cm,rightskip=4cm]
    { \inferrule*[right={\scriptsize (Q:Break)},leftskip=0cm,rightskip=0cm]
      { }
      { (x {<} 10, B^\text{br}); (x {<} 10,Q^\text{br}) \vdash
        \code{break} \dashv (\bot,P^\text{br})
      }
    }
    { (x {<} 10, B^\text{el}); (x {<} 10,Q^\text{el}) \vdash
      \code{break} \dashv (\cdot,P^\text{el})
    }
  }
  { \hspace{3cm} (x {<} 10, B^\text{lo}); (\cdot,Q^\text{lo}) \vdash
    \loopbody \dashv (\cdot,P^\text{lo}) \hspace{3cm}
  }
}
{ (\cdot, B); (\cdot, Q) \vdash \code{loop}~{\loopbody} \dashv (x {<} 10, P)
}
\vspace{-.3cm}
\end{mathpar}
\flushleft
\begin{tabular}{l}Constraints:\end{tabular}
\vspace{-.2cm}
$$
\begin{array}{lll}
P {=} B^\text{lo} \land Q {=} Q^\text{lo} {=} P^\text{lo}
& B^\text{el} {=} B^\text{if} {=} B^\text{lo}
    \land Q^\text{el} {=} Q^\text{if} {=} Q^\text{lo}
    \land P^\text{el} {=} P^\text{if} {=} P^\text{lo}
& B^\text{el} {=} B^\text{br} \land Q^\text{el} \succeq_{(x{<}10)} Q^\text{br}
    \land P^\text{br} \succeq_{(\cdot)} P^\text{el}
\\
B^\text{br} {=} Q^\text{br}
& B^\text{if} {=} B^\text{sq} \land Q^\text{if} \succeq_{(x{<}10)} Q^\text{sq}
    \land P^\text{sq} \succeq_{(\cdot)} P^\text{if}
& B^\text{sq} {=} B^\text{we} {=} B^\text{ti} \land Q^\text{sq} {=} Q^\text{we}
    \land P^\text{we} {=} Q^\text{ti} \land P^\text{ti} {=} P^\text{sq}
\\
Q^\text{ti} {=} P^\text{ti} + 5
& B^\text{we} {=} B^\text{de} \land Q^\text{we} \succeq_{(x{<}10)} Q^\text{de}
    \land P^\text{de} \succeq_{(\cdot)} P^\text{we}
& p^\text{de}_{0,10} {=} q^\text{de}_{0,10} + q^\text{de}_{0,x}
    \land p^\text{de}_{0} {=} q^\text{de}_{0}
    \land \forall (\alpha, \beta) \neq (0,10)  . \,
              p^\text{de}_{\alpha,\beta} {=} q^\text{de}_{\alpha,\beta}
\end{array}
$$
\begin{tabular}{l@{\hspace{5em}}l}
  Linear Objective Function: $
    1{\cdot}q_{x,0} + 10000{\cdot}q_{0,x} + 11{\cdot}q_{x,10} + 9990{\cdot}q_{10,x}
  $
& Constant Objective Function: $
    1{\cdot}q_0 + 11{\cdot}q_{0,10}
  $
\end{tabular}
\vspace{.1cm}
\caption{An example derivation as produced by the automatic tool.}
\label{fig:derivation}
\end{figure*}

>>>>

while (x<n) {
  ${\color{blue}%
  x{<}n; \, |[x, n]| {+} |[z, n]| \vdash }$
  if (z>x)
    ${\color{blue}%
    x{<}n; \, |[x, n]| {+} |[z, n]| \vdash }$
    x=x+1;
    ${\color{blue}%
    \dashv \cdot; \, 1 {+} |[x, n]| {+} |[z, n]| }$
  else
    ${\color{blue}%
    z{\leq}x, x{<}n; \, |[x, n]| {+} |[z, n]| \vdash }$
    z=z+1;
    ${\color{blue}%
    \dashv \cdot; \, 1 {+} |[x, n]| {+} |[z, n]| }$
  ${\color{blue}%
  \dashv \cdot; \, 1 {+} |[x, n]| {+} |[z, n]| \vdash }$
  tick(1);
  ${\color{blue}%
  \dashv \cdot; \, |[x, n]| {+} |[z, n]| }$
  }
   \end{lstlisting}
\vspace{-2.5ex}
$|[x, n]| + |[z, n]|$
\\[.4\baselineskip]
      {\bf speed\_2}
    \end{center}
  \end{minipage}
%
\hfill
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
while (z-y>0) {
  ${\color{blue}%
  y{<}z; \, 3.1|[y,z]| {+} 0.1|[0,y]| \vdash }$
  y=y+1;
  ${\color{blue}%
  \dashv \cdot; \, 3 {+} 3.1|[y,z]| {+} 0.1|[0,y]| \vdash }$
  tick(3);
  ${\color{blue}%
  \dashv \cdot; \, 3.1|[y,z]| {+} 0.1|[0,y]| }$
}
${\color{blue}%
\dashv \cdot; \, 3.1|[y,z]| {+} 0.1|[0,y]| \vdash }$
while (y>9) {
  ${\color{blue}%
  y{>}9; \, 3.1|[y,z]| {+} 0.1|[0,y]| \vdash }$
  y=y-10;
  ${\color{blue}%
  \dashv \cdot; \, 1 {+} 3.1|[y,z]| {+} 0.1|[0,y]| \vdash }$
  tick(1);
  ${\color{blue}%
  \dashv \cdot; \, 3.1|[y,z]| {+} 0.1|[0,y]| }$
}
   \end{lstlisting}
\vspace{-2.5ex}
$3.1|[y,z]| + 0.1|[0,y]|$
\\[.4\baselineskip]
      {\bf t08a}
    \end{center}
  \end{minipage}
%
\hfill
%
%
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}
while (n<0) {
  ${\color{blue}%
  n{<}0; \,  P(n,y) \vdash }$
  n=n+1;
  ${\color{blue}%
  \dashv \cdot; \,  59 {+} P(n,y) \vdash }$
  y=y+1000;
  ${\color{blue}%
  \dashv \cdot; \, 9 {+} P(n,y) \vdash }$
  while (y>=100 && *){
    ${\color{blue}%
    y{>}99; \, 9 {+} P(n,y) \vdash }$
    y=y-100;
    ${\color{blue}%
    \dashv \cdot; \, 14 {+} P(n,y) \vdash }$
    tick(5);
  } ${\color{blue}%
  \dashv \cdot; \, 9 {+} P(n,y) \vdash }$
  tick(9);
  ${\color{blue}%
  \dashv \cdot; \, P(n,y) }$
}
   \end{lstlisting}
\vspace{-2.5ex}
$59|[n,0]| {+} 0.05|[0,y]|$
\\[.4\baselineskip]
      {\bf t27}
    \end{center}
  \end{minipage}
\vspace{1ex}
\caption{Derivations of bounds on the number of ticks for challenging
  examples.  Examples \emph{speed\_1} and \emph{speed\_2}
  (from~\cite{GulwaniMC09}) use \emph{tricky iteration patterns},
  \emph{t08a} contains \emph{sequential loops} so that the iterations
  of the second loop depend on the first, and \emph{t27} contains
  interacting \emph{nested loops}. \iffull{In the potential functions, we only
  mention the non-zero terms and in the logical context $\Gamma$ we
  only mention assertions that we use.}{} In
  Example \emph{t27}, we use the abbreviation $P(n,y) := 59|[n,0]| {+}
  0.05|[0,y]|$.}
  \label{fig:ex_list}
\end{figure*}

@@

\ifshort{
\begin{figure*}
\small
\vspace{-.6cm}
\def \MathparLineskip {\lineskip=0.35cm}
\begin{mathpar}
\Rule{Q:Update}
{ q'_{xy}, q'_{yx} \in \Qplusz
\\ \forall u. (q_{yu} = q'_{xu} + q'_{yu} \land q_{uy} = q'_{ux} + q'_{uy})
}
{ B; R; (\Gamma[x/y], Q {+} M_u {+} M_e(y)) \vdash x \gets y \dashv (\Gamma, Q') }
%
\and \Rule[leftskip=.1cm,rightskip=.1cm]{Q:Loop}
{ (\Gamma', Q'); R; (\Gamma,Q) \vdash S \dashv (\Gamma,  Q {+} M_l) }
{ B; R; (\Gamma, Q) \vdash \code{loop}~S \dashv (\Gamma', Q') }
%
\\ \Rule[leftskip=1cm,rightskip=.5cm]{Q:IncP}
{ \Gamma \models y \ge 0 \!
\\ \mathcal U = \left\{ u \mid \Gamma \models x + y \in \inter x u \right\} \!
\\\\ \textstyle q'_{0y} = q_{0y}
      + \sum_{u \in \mathcal U} q_{xu}
      - \sum_{v \not\in \mathcal U} q_{vx} \!
}
{ \textstyle
  B; R; (\Gamma[x/x {+} y], Q {+} M_u {+} M_e(x {+} y)) \vdash x \gets x + y \dashv (\Gamma, Q')
}
%
\and \Rule[leftskip=.5cm,rightskip=1cm]{Q:Inc}
{ M = M_u + M_e(x {\pm} y)
\\\\ \textstyle q'_{0y} = q_{0y} - \sum_{v} q_{vx}
\\ \textstyle q'_{y0} = q_{y0} - \sum_{v} q_{xv}
}
{ \textstyle
  B; R; (\Gamma[x/x {\pm} y], Q {+} M) \vdash x \gets x \pm y \dashv (\Gamma, Q')
}
%
\\ \Rule{Q:Seq}
{  B; R; (\Gamma, Q) \vdash S_1 \dashv (\Gamma', Q' {+} M_s)
\\\\ B; R; (\Gamma', Q') \vdash S_2 \dashv (\Gamma'',Q'')
}
{ B; R; (\Gamma, Q) \vdash S_1;S_2 \dashv (\Gamma'',Q'') }
%
\and \Rule{Q:Weak}
{ B; R; (\Gamma_2,Q_2) \vdash S \dashv (\Gamma'_2, Q'_2)
\\ \!\! \Gamma_1 \models \Gamma_2
\\\\ Q_1 \succeq_{\Gamma_1} Q_2
\\ \Gamma'_2 \models \Gamma'_1
\\ Q'_2 \succeq_{\Gamma_2'} Q'_1
}
{ B; R; (\Gamma_1,Q_1) \vdash S \dashv (\Gamma'_1, Q'_1) }
%
\\ \Rule{Relax}
{ \mathcal L = \{ xy \mid \exists l_{xy} {\in} \N \, . \, \Gamma \models l_{xy} \le |\inter x y| \}
\\ \mathcal U = \{ xy \mid \exists u_{xy}{\in} \N \, . \, \Gamma \models |\inter x y| \le u_{xy} \}
\\\\ \forall i \in \mathcal U.\, q'_i \ge q_i - r_i
\\ \forall i \in \mathcal L.\, q'_i \ge q_i + p_i
\\ \forall i \not\in \mathcal U {\cup} \mathcal L {\cup} \{0\} .\, q'_i \ge q_i
\\ q'_0 \geq q_0 {\textstyle + \sum_{i \in \mathcal U} u_i r_i - \sum_{i \in \mathcal L} l_i p_i}
}
{ Q' \succeq_\Gamma Q }
\vspace{-.3cm}
\end{mathpar}
\caption{Selected inference rules of the quantitative analysis.}
\label{fig:auto}
\end{figure*}
}{}

@@

\paraskip
\paragraph{Function Specifications.}

\jan{Here we have to say something about function specifications and
  function calls.}
\jan{Here we have to say something about function specifications and
  function calls.}
\jan{Here we have to say something about function specifications and
  function calls.}
\jan{Here we have to say something about function specifications and
  function calls.}
\jan{Here we have to say something about function specifications and
  function calls.}
\jan{Here we have to say something about function specifications and
  function calls.}

@@

\newcommand{\loopbody}[0]{\ensuremath{\code{if~(x - 10 \geq 0)~\{x=x{-}10; tick(5);\}~else~break;}}}
\begin{figure*}
\vspace{-.6cm}
\centering
\footnotesize
\begin{mathpar}
\inferrule*[right={\scriptsize (Q:Loop)},leftskip=0cm,rightskip=0cm,width=20cm]
{ \inferrule*[right={\scriptsize (Q:If)},leftskip=0cm,rightskip=0cm,width=20cm]
  { \inferrule*[right={\scriptsize (Q:Weak)},leftskip=2cm,rightskip=4cm, vdots=1cm]
    { \inferrule*[right={\scriptsize (Q:Seq)},leftskip=0cm,rightskip=0cm]
      { \inferrule*[right={\scriptsize (Q:Weak)},leftskip=0cm,rightskip=0cm]
        { \inferrule*[right={\scriptsize (Q:DecP)},leftskip=0cm,rightskip=0cm]
          {
          }
          { (x {<} 10, B^\text{de}); ((x {\geq} 10,Q^\text{de})  \vdash \code{x = x - 10}
            \dashv (\cdot, P^\text{de})
          }
        }
        { (x {<} 10, B^\text{we}); ((x {\geq} 10,Q^\text{we})  \vdash \code{x = x - 10}
          \dashv (\cdot, P^\text{we})
        }
        \and
        \inferrule*[right={\scriptsize (Q:Tick)},leftskip=0cm,rightskip=0cm]
        {
        }
        { (x {<} 10, B^\text{ti}); (\cdot,Q^\text{ti})  \vdash \code{tick(5)}
          \dashv (\cdot, P^\text{ti})
        }
      }
      { (x {<} 10, B^\text{sq}); ((x {\geq} 10,Q^\text{sq}) \vdash
        \code{x=x{-}10; tick(5);} \dashv (\cdot,P^\text{sq})
      }
    }
    { (x {<} 10, B^\text{if}); ((x {\geq} 10,Q^\text{if}) \vdash
      \code{x=x{-}10; tick(5);} \dashv (\cdot,P^\text{if})
    }
    \and
    \inferrule*[right={\scriptsize (Q:Weak)},leftskip=4.5cm,rightskip=4cm]
    { \inferrule*[right={\scriptsize (Q:Break)},leftskip=0cm,rightskip=0cm]
      { }
      { (x {<} 10, B^\text{br}); (x {<} 10,Q^\text{br}) \vdash
        \code{break} \dashv (\bot,P^\text{br})
      }
    }
    { (x {<} 10, B^\text{el}); (x {<} 10,Q^\text{el}) \vdash
      \code{break} \dashv (\cdot,P^\text{el})
    }
  }
  { \hspace{3cm} (x {<} 10, B^\text{lo}); (\cdot,Q^\text{lo}) \vdash
    \loopbody \dashv (\cdot,P^\text{lo}) \hspace{3cm}
  }
}
{ (\cdot, B); (\cdot, Q) \vdash \code{loop}~{\loopbody} \dashv (x {<} 10, P)
}
\vspace{-.3cm}
\end{mathpar}
\flushleft
\begin{tabular}{l}Constraints:\end{tabular}
\vspace{-.2cm}
$$
\begin{array}{lll}
P {=} B^\text{lo} \land Q {=} Q^\text{lo} {=} P^\text{lo}
& B^\text{el} {=} B^\text{if} {=} B^\text{lo}
    \land Q^\text{el} {=} Q^\text{if} {=} Q^\text{lo}
    \land P^\text{el} {=} P^\text{if} {=} P^\text{lo}
& B^\text{el} {=} B^\text{br} \land Q^\text{el} \succeq_{(x{<}10)} Q^\text{br}
    \land P^\text{br} \succeq_{(\cdot)} P^\text{el}
\\
B^\text{br} {=} Q^\text{br}
& B^\text{if} {=} B^\text{sq} \land Q^\text{if} \succeq_{(x{<}10)} Q^\text{sq}
    \land P^\text{sq} \succeq_{(\cdot)} P^\text{if}
& B^\text{sq} {=} B^\text{we} {=} B^\text{ti} \land Q^\text{sq} {=} Q^\text{we}
    \land P^\text{we} {=} Q^\text{ti} \land P^\text{ti} {=} P^\text{sq}
\\
Q^\text{ti} {=} P^\text{ti} + 5
& B^\text{we} {=} B^\text{de} \land Q^\text{we} \succeq_{(x{<}10)} Q^\text{de}
    \land P^\text{de} \succeq_{(\cdot)} P^\text{we}
& p^\text{de}_{0,10} {=} q^\text{de}_{0,10} + q^\text{de}_{0,x}
    \land p^\text{de}_{0} {=} q^\text{de}_{0}
    \land \forall (\alpha, \beta) \neq (0,10)  . \,
              p^\text{de}_{\alpha,\beta} {=} q^\text{de}_{\alpha,\beta}
\end{array}
$$
\begin{tabular}{l@{\hspace{5em}}l}
  Linear Objective Function: $
    1{\cdot}q_{x,0} + 10000{\cdot}q_{0,x} + 11{\cdot}q_{x,10} + 9990{\cdot}q_{10,x}
  $
& Constant Objective Function: $
    1{\cdot}q_0 + 11{\cdot}q_{0,10}
  $
\end{tabular}
\vspace{.1cm}
\caption{An example derivation as produced by the automatic tool.}
\label{fig:derivation}
\end{figure*}
